---
output: rmarkdown::github_document
bibliography: "README-refs.bib"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R/`tmle3adapt`

[![Travis-CI Build Status](https://travis-ci.org/tlverse/tmle3adapt.svg?branch=master)](https://travis-ci.org/tlverse/tmle3adapt)
[![AppVeyor Build  Status](https://ci.appveyor.com/api/projects/status/github/tlverse/tmle3adapt?branch=master&svg=true)](https://ci.appveyor.com/project/podTockom/tmle3adapt)
[![Coverage Status](https://img.shields.io/codecov/c/github/tlverse/tmle3adapt/master.svg)](https://codecov.io/github/tlverse/tmle3adapt?branch=master)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](http://www.gnu.org/licenses/gpl-3.0)

> Targeted Sequential Designs for Learning the Optimal Treatment Rule or Average
> Treatment Effect from Optimal Surrogate Outcomes

__Authors:__ [Ivana Malenica](https://github.com/podTockom), and [Mark van der
Laan](https://vanderlaan-lab.org)

# What's `tmle3adapt`?

The goal of `tmle3adapt` is to ...

---

## Installation

You can install the development version of `tmle3shift` from GitHub via
[`devtools`](https://www.rstudio.com/products/rpackages/devtools/) with

```{r gh-installation, eval = FALSE}
devtools::install_github("tlverse/tmle3adapt")
```

---

## Issues

If you encounter any bugs or have any specific feature requests, please [file an
issue](https://github.com/tlverse/tmle3adapt/issues).

---

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# basic example code goes here
```

---

## License

The contents of this repository are distributed under the GPL-3 license. See
file `LICENSE` for details.

---

## References

